A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array

### 2014-11-14 ms.tex
Renamed figure file names, moved them to parent older and removed separate figures folder

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/fourier_space_185.0_MHz_30.7_MHz.eps}
\caption{Fourier space in which delay (and power) spectra of EoR H{\sc i} signals are presented. The $x$--axis is denoted by $|\vec{b}|$ (antenna spacing) or $k_\perp$ (transverse wavenumber). The $y$--axis denoted by $\tau$ (delay) or $k_\parallel$ (line--of--sight wavenumber). Here, $k_\perp$ and $k_\parallel$ are obtained for a frequency of 185~MHz. The dark shaded region is referred to as the {\it foreground wedge} where smooth spectrum foregrounds reside. Its boundaries (solid lines), given by light travel time for corresponding antenna spacings, are referred to as horizon delay limits. Regions excluding the {\it wedge} and narrow extensions of the {\it wedge} (white unshaded strips) caused by convolution with the instrumental transfer function are expected to be relatively free of foreground contamination. Due to an undesirable grating pattern (dot--dashed lines) of the instrument used in this study, namely the MWA, we conservatively identify a restricted region of high EoR sensitivity (medium shade) and refer to it as the {\it EoR window} in this paper. \label{fig:fourier-space}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/custom_pointings.eps}
\caption{MWA tile beam pointing directions during the course of the observation. The $x$--axis refers to the {\it local sidereal time} (LST). The axis on the left refers to longitudes, namely, Right Ascension (RA) and Hour Angle (HA). Negative values of RA, HA, and LST are to be interpreted as having been wrapped around by 360\arcdeg~ or 24 hours. The axis on the right refers to the declination of the pointing direction. The RA, HA, and declination are plotted with solid, dashed and dotted lines respectively. The sky is allowed to drift for $\sim 30$~mins before the beamformer delay settings change in a discrete step to center the beam around RA = 0$^\textrm{h}$, Dec = $-30$\arcdeg. Dot--dashed vertical lines show the LST of {\it off-zenith} and {\it zenith} pointings used in our study. \label{fig:pointings}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/multi_baseline_fhd_delay_spectrum_snapshots.eps}
\caption{Delay spectra of two observations of the EoR field (RA = 0$^\textrm{h}$, Dec = $-30$\arcdeg) at an {\it off--zenith} pointing (top) when tiles have significant secondary lobes in the direction of the Galactic center and a {\it zenith} pointing (bottom) where secondary lobes are minimal and the Galaxy has set. For reference, the $k$--space equivalent of $\tau$ and $|\vec{b}|$, namely, $k_\parallel$ and $k_\perp$ are shown at the axes on the right and top respectively. White lines mark the boundaries of {\it foreground wedge} determined by light travel time across each baseline. Smooth spectrum objects predominantly reside in this {\it foreground wedge}. The logarithmic color scale (shown at the right) is common to both panels. \label{fig:fhd_data}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/delta_array_powerpattern_0.3m_ground_custom.eps}
\caption{Models of MWA tile power--pattern for {\it off--zenith} (top) and {\it zenith} pointings (bottom) at 185~MHz. An MWA tile is modeled as a 4$\times$4 array of isotropic radiators placed 0.3~m above an infinite ground plane. Random fluctuations of rms 0.05~ns have been added to delay corrections during the phased addition of voltages from these isotropic radiators. The logarithmic color scale (shown on the right) is common to both panels. \label{fig:power_pattern}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/dsm.eps}
\caption{Sky brightness temperature of the diffuse foreground model at 185~MHz visible during {\it off--zenith} (top) and {\it zenith} (bottom) pointings. The color scale on the right is logarithmic and is common to both panels. Contours of power--pattern shown in Figure~\ref{fig:power_pattern} are overlaid. The contour levels shown are 0.00195, 0.00781, 0.0312, 0.125, and 0.5. The Galactic center and a portion of the Galactic plane are prominently visible during the {\it off--zenith} pointing and the MWA tile power gain is significant ($\gtrsim 12$\%) in that direction. In contrast, emission from the Galactic plane in {\it zenith} pointing is significantly lesser. \label{fig:DSM}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/csm.eps}
\caption{Flux densities of bright point sources at 185~MHz visible during {\it off--zenith} (top) and {\it zenith} (bottom) pointings. The color scale on the right is logarithmic and is common to both panels and corresponds to the color--coded filled circles. Contours of power--pattern shown in Figure~\ref{fig:power_pattern} are overlaid. The contour levels shown are 0.001953125, 0.0078125, 0.03125, 0.125, and 0.5. \label{fig:CSM}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/multi_baseline_sim_delay_spectrum_snapshots.eps}
\caption{Same as Figure~\ref{fig:fhd_data}, but generated from simulated visibilities using the model described in \S\ref{sec:modeling}. Note the similarity between the broad features to those in Figure~\ref{fig:fhd_data}. \label{fig:sim_data}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/delta_array_multi_baseline_CLEAN_noiseless_visibilities_0.3m_ground_custom_gaussian_FG_model_dsm_all_sky_nside_64_Tsys_95.0K_185.0_MHz_30.7_MHz_bhw2.0.eps}
\caption{Simulated delay spectrum amplitudes $|V_{b\tau}(\vec{b},\tau)|$ (in units of Jy~Hz) for {\it off--zenith} (top) and {\it zenith} (bottom) pointings for the diffuse foreground model without any thermal noise. White lines mark the boundaries of the {\it foreground wedge} determined by the horizon delay limit and antenna spacing. The axes and color scale are identical to those in Figures~\ref{fig:fhd_data} and \ref{fig:sim_data}. In the {\it zenith} pointing, delay spectrum from diffuse emission has a {\it two--pronged fork}--shaped structure and is present even at wide antenna spacings. \label{fig:noiseless-dsm-delay-spectrum}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/delta_array_multi_baseline_CLEAN_noiseless_visibilities_0.3m_ground_custom_gaussian_FG_model_csm_all_sky_nside_64_Tsys_95.0K_185.0_MHz_30.7_MHz_bhw2.0.eps}
\caption{Same as Figure~\ref{fig:noiseless-dsm-delay-spectrum} but for a foreground model consisting of compact emission. Compact emission gives rise to centrally concentrated features and stays flat across antenna spacings in the {\it foreground wedge}.\label{fig:noiseless-csm-delay-spectrum}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/delta_array_3_baseline_comparison_CLEAN_noiseless_visibilities_0.3m_ground_custom_gaussian_FG_model_all_sky_nside_64_Tsys_95.0K_185.0_MHz_30.7_MHz_bhw2.0.eps}
\caption{Simulated delay spectrum amplitudes $|V_{b\tau}(\vec{b},\tau)|$ for three chosen northward oriented antenna spacings of length: $\sim$84~m ({\it top}), $\sim$104~m ({\it middle}), and $\sim$171~m ({\it bottom}). The antenna spacing is specified in each panel along East, North and Upward directions. The solid red, cyan, and black lines denote contributions from diffuse, compact, and composite foreground models respectively. Vertical dotted lines mark the horizon delay limits. The shaded region denotes the envelope of uncertainty around the composite model delay spectrum. This uncertainty is dictated by uncertainties in spectral indices of foreground models inside the delay horizon delay limits. Outside the horizon delay limits, it is predominantly due to thermal noise fluctuations. Compact emission dominates the central regions of delay spectrum while both components, especially diffuse emission on short antenna spacings, dominate near the horizon delay limits, giving rise to a {\it pitchfork}--shaped structure. \label{fig:pitchfork-baselines}}
\end{figure}

@@

\begin{figure*}[htb]
\centering
\subfloat[][Sky model]{\label{fig:sky-model}\includegraphics[width=0.33\linewidth]{figures/v1_0/sky_model_snapshot_0.eps}}
\subfloat[][Delay maps]{\label{fig:delay-map}\includegraphics[width=0.33\linewidth]{figures/v1_0/directional_delay_map_snapshot_0.eps}}
\subfloat[][Delay Spectra]{\label{fig:baseline-breakup}\includegraphics[width=0.33\linewidth]{figures/v1_0/baseline_orientation_breakup_snapshot_0.eps}}
\caption{(a): Sky model showing compact ({\it top}) and diffuse ({\it bottom}) emission. Contours of power pattern are overlaid whose levels are identical to those in Figures~\ref{fig:DSM} and \ref{fig:CSM}. The Galactic center is very prominent in diffuse emission in the western sky and is co--located with a bright secondary lobe of the power pattern. (b): Sky hemisphere mapped to delays observed on antenna spacings with northward ({\it top}) and eastward ({\it bottom}) orientations. Color scale shown is for a 100~m antenna spacing. Delays vary linearly with antenna spacing length. The bright Galactic center in the western sky is recorded at zero delays in northward antenna spacings and close to negative horizon delay limit on eastward antenna spacings. (c): Simulated delay spectra $|V_{b\tau}(\vec{b},\tau)|$ on antenna spacings oriented northward ({\it top}) and eastward ({\it bottom}). White lines denote horizon delay limits. The bright Galactic center is prominently visible close to negative horizon delay limit, especially on short eastward antenna spacings. These are also the most severely contaminated by foreground spillover. The northward antenna spacings, on the other hand, are the least contaminated.}
\label{fig:breakup}
\end{figure*}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/baseline_screening_before_after_nside_64_Tsys_95.0K.eps}
\caption{Simulated delay spectra amplitudes $|V_{b\tau}(\vec{b},\tau)|$ for the {\it off--zenith} pointing with all antenna spacings included ({\it top}) and with short eastward antenna spacings discarded ({\it bottom}). Discarded antenna spacings (black vertical stripes) have lengths $|\vec{b}|<30$~m (leftward of vertical dashed line) and orientations $|\theta_\textrm{b}|<$~22\fdg 5. The spillover from the bright Galactic center near the negative horizon delay limit from the {\it foreground wedge} prominent when all antenna spacings are used is lowered by an order of magnitude when short eastward antenna spacings are discarded. Color scale has been adjusted to emphasize mitigation achieved in foreground contamination. \label{fig:before-after}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{figures/v1_0/baseline_screening_nside_64_Tsys_95.0K.eps}
\caption{Drop in foreground contamination in the {\it EoR window}, and loss of data for the {\it off--zenith} pointing as a function of discarded baselines. Eastward baselines with varying degrees of directedness -- $|\theta_\textrm{b}|<$~7\fdg 5 (solid circles), $|\theta_\textrm{b}|<$~15\arcdeg~ (solid squares), and $|\theta_\textrm{b}|<$~22\fdg 5 (solid stars) -- and lengths $|\vec{b}| \le |\vec{b}|_\textrm{max}$ ($x$--axis) are discarded. Loss of data (dotted lines) is measured by discarded baselines as a fraction of the total number for the corresponding cases. Foreground contamination in the {\it EoR window} (solid lines) drops by a factor $\sim$1.5 ($|\theta_\textrm{b}|\le$~7\fdg 5) to $\sim$10 ($|\theta_\textrm{b}|\le$~22\fdg 5). The latter limit can be achieved with a mere 5\% loss of data at $|\vec{b}|_\textrm{max}\simeq30$~m, and discarding longer baselines ($|\vec{b}|\gtrsim 30$~m) has no effect in further reducing foreground contamination. \label{fig:screening}}
\end{figure}

>>>>

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/fourier_space_185.0_MHz_30.7_MHz.eps}
\includegraphics[width=\linewidth]{f1.eps}
\caption{Fourier space in which delay (and power) spectra of EoR H{\sc i} signals are presented. The $x$--axis is denoted by $|\vec{b}|$ (antenna spacing) or $k_\perp$ (transverse wavenumber). The $y$--axis denoted by $\tau$ (delay) or $k_\parallel$ (line--of--sight wavenumber). Here, $k_\perp$ and $k_\parallel$ are obtained for a frequency of 185~MHz. The dark shaded region is referred to as the {\it foreground wedge} where smooth spectrum foregrounds reside. Its boundaries (solid lines), given by light travel time for corresponding antenna spacings, are referred to as horizon delay limits. Regions excluding the {\it wedge} and narrow extensions of the {\it wedge} (white unshaded strips) caused by convolution with the instrumental transfer function are expected to be relatively free of foreground contamination. Due to an undesirable grating pattern (dot--dashed lines) of the instrument used in this study, namely the MWA, we conservatively identify a restricted region of high EoR sensitivity (medium shade) and refer to it as the {\it EoR window} in this paper. \label{fig:fourier-space}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/custom_pointings.eps}
\includegraphics[width=\linewidth]{f2.eps}
\caption{MWA tile beam pointing directions during the course of the observation. The $x$--axis refers to the {\it local sidereal time} (LST). The axis on the left refers to longitudes, namely, Right Ascension (RA) and Hour Angle (HA). Negative values of RA, HA, and LST are to be interpreted as having been wrapped around by 360\arcdeg~ or 24 hours. The axis on the right refers to the declination of the pointing direction. The RA, HA, and declination are plotted with solid, dashed and dotted lines respectively. The sky is allowed to drift for $\sim 30$~mins before the beamformer delay settings change in a discrete step to center the beam around RA = 0$^\textrm{h}$, Dec = $-30$\arcdeg. Dot--dashed vertical lines show the LST of {\it off-zenith} and {\it zenith} pointings used in our study. \label{fig:pointings}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/multi_baseline_fhd_delay_spectrum_snapshots.eps}
\includegraphics[width=\linewidth]{f3.eps}
\caption{Delay spectra of two observations of the EoR field (RA = 0$^\textrm{h}$, Dec = $-30$\arcdeg) at an {\it off--zenith} pointing (top) when tiles have significant secondary lobes in the direction of the Galactic center and a {\it zenith} pointing (bottom) where secondary lobes are minimal and the Galaxy has set. For reference, the $k$--space equivalent of $\tau$ and $|\vec{b}|$, namely, $k_\parallel$ and $k_\perp$ are shown at the axes on the right and top respectively. White lines mark the boundaries of {\it foreground wedge} determined by light travel time across each baseline. Smooth spectrum objects predominantly reside in this {\it foreground wedge}. The logarithmic color scale (shown at the right) is common to both panels. \label{fig:fhd_data}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/delta_array_powerpattern_0.3m_ground_custom.eps}
\includegraphics[width=\linewidth]{f4.eps}
\caption{Models of MWA tile power--pattern for {\it off--zenith} (top) and {\it zenith} pointings (bottom) at 185~MHz. An MWA tile is modeled as a 4$\times$4 array of isotropic radiators placed 0.3~m above an infinite ground plane. Random fluctuations of rms 0.05~ns have been added to delay corrections during the phased addition of voltages from these isotropic radiators. The logarithmic color scale (shown on the right) is common to both panels. \label{fig:power_pattern}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/dsm.eps}
\includegraphics[width=\linewidth]{f5.eps}
\caption{Sky brightness temperature of the diffuse foreground model at 185~MHz visible during {\it off--zenith} (top) and {\it zenith} (bottom) pointings. The color scale on the right is logarithmic and is common to both panels. Contours of power--pattern shown in Figure~\ref{fig:power_pattern} are overlaid. The contour levels shown are 0.00195, 0.00781, 0.0312, 0.125, and 0.5. The Galactic center and a portion of the Galactic plane are prominently visible during the {\it off--zenith} pointing and the MWA tile power gain is significant ($\gtrsim 12$\%) in that direction. In contrast, emission from the Galactic plane in {\it zenith} pointing is significantly lesser. \label{fig:DSM}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/csm.eps}
\includegraphics[width=\linewidth]{f6.eps}
\caption{Flux densities of bright point sources at 185~MHz visible during {\it off--zenith} (top) and {\it zenith} (bottom) pointings. The color scale on the right is logarithmic and is common to both panels and corresponds to the color--coded filled circles. Contours of power--pattern shown in Figure~\ref{fig:power_pattern} are overlaid. The contour levels shown are 0.001953125, 0.0078125, 0.03125, 0.125, and 0.5. \label{fig:CSM}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/multi_baseline_sim_delay_spectrum_snapshots.eps}
\includegraphics[width=\linewidth]{f7.eps}
\caption{Same as Figure~\ref{fig:fhd_data}, but generated from simulated visibilities using the model described in \S\ref{sec:modeling}. Note the similarity between the broad features to those in Figure~\ref{fig:fhd_data}. \label{fig:sim_data}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/delta_array_multi_baseline_CLEAN_noiseless_visibilities_0.3m_ground_custom_gaussian_FG_model_dsm_all_sky_nside_64_Tsys_95.0K_185.0_MHz_30.7_MHz_bhw2.0.eps}
\includegraphics[width=\linewidth]{f8.eps}
\caption{Simulated delay spectrum amplitudes $|V_{b\tau}(\vec{b},\tau)|$ (in units of Jy~Hz) for {\it off--zenith} (top) and {\it zenith} (bottom) pointings for the diffuse foreground model without any thermal noise. White lines mark the boundaries of the {\it foreground wedge} determined by the horizon delay limit and antenna spacing. The axes and color scale are identical to those in Figures~\ref{fig:fhd_data} and \ref{fig:sim_data}. In the {\it zenith} pointing, delay spectrum from diffuse emission has a {\it two--pronged fork}--shaped structure and is present even at wide antenna spacings. \label{fig:noiseless-dsm-delay-spectrum}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/delta_array_multi_baseline_CLEAN_noiseless_visibilities_0.3m_ground_custom_gaussian_FG_model_csm_all_sky_nside_64_Tsys_95.0K_185.0_MHz_30.7_MHz_bhw2.0.eps}
\includegraphics[width=\linewidth]{f9.eps}
\caption{Same as Figure~\ref{fig:noiseless-dsm-delay-spectrum} but for a foreground model consisting of compact emission. Compact emission gives rise to centrally concentrated features and stays flat across antenna spacings in the {\it foreground wedge}.\label{fig:noiseless-csm-delay-spectrum}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/delta_array_3_baseline_comparison_CLEAN_noiseless_visibilities_0.3m_ground_custom_gaussian_FG_model_all_sky_nside_64_Tsys_95.0K_185.0_MHz_30.7_MHz_bhw2.0.eps}
\includegraphics[width=\linewidth]{f10.eps}
\caption{Simulated delay spectrum amplitudes $|V_{b\tau}(\vec{b},\tau)|$ for three chosen northward oriented antenna spacings of length: $\sim$84~m ({\it top}), $\sim$104~m ({\it middle}), and $\sim$171~m ({\it bottom}). The antenna spacing is specified in each panel along East, North and Upward directions. The solid red, cyan, and black lines denote contributions from diffuse, compact, and composite foreground models respectively. Vertical dotted lines mark the horizon delay limits. The shaded region denotes the envelope of uncertainty around the composite model delay spectrum. This uncertainty is dictated by uncertainties in spectral indices of foreground models inside the delay horizon delay limits. Outside the horizon delay limits, it is predominantly due to thermal noise fluctuations. Compact emission dominates the central regions of delay spectrum while both components, especially diffuse emission on short antenna spacings, dominate near the horizon delay limits, giving rise to a {\it pitchfork}--shaped structure. \label{fig:pitchfork-baselines}}
\end{figure}

@@

\begin{figure*}[htb]
\centering
% \subfloat[][Sky model]{\label{fig:sky-model}\includegraphics[width=0.33\linewidth]{figures/v1_0/sky_model_snapshot_0.eps}}
% \subfloat[][Delay maps]{\label{fig:delay-map}\includegraphics[width=0.33\linewidth]{figures/v1_0/directional_delay_map_snapshot_0.eps}}
% \subfloat[][Delay Spectra]{\label{fig:baseline-breakup}\includegraphics[width=0.33\linewidth]{figures/v1_0/baseline_orientation_breakup_snapshot_0.eps}}
\subfloat[][Sky model]{\label{fig:sky-model}\includegraphics[width=0.33\linewidth]{f11a.eps}}
\subfloat[][Delay maps]{\label{fig:delay-map}\includegraphics[width=0.33\linewidth]{f11b.eps}}
\subfloat[][Delay Spectra]{\label{fig:baseline-breakup}\includegraphics[width=0.33\linewidth]{f11c.eps}}
\caption{(a): Sky model showing compact ({\it top}) and diffuse ({\it bottom}) emission. Contours of power pattern are overlaid whose levels are identical to those in Figures~\ref{fig:DSM} and \ref{fig:CSM}. The Galactic center is very prominent in diffuse emission in the western sky and is co--located with a bright secondary lobe of the power pattern. (b): Sky hemisphere mapped to delays observed on antenna spacings with northward ({\it top}) and eastward ({\it bottom}) orientations. Color scale shown is for a 100~m antenna spacing. Delays vary linearly with antenna spacing length. The bright Galactic center in the western sky is recorded at zero delays in northward antenna spacings and close to negative horizon delay limit on eastward antenna spacings. (c): Simulated delay spectra $|V_{b\tau}(\vec{b},\tau)|$ on antenna spacings oriented northward ({\it top}) and eastward ({\it bottom}). White lines denote horizon delay limits. The bright Galactic center is prominently visible close to negative horizon delay limit, especially on short eastward antenna spacings. These are also the most severely contaminated by foreground spillover. The northward antenna spacings, on the other hand, are the least contaminated.}
\label{fig:breakup}
\end{figure*}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/baseline_screening_before_after_nside_64_Tsys_95.0K.eps}
\includegraphics[width=\linewidth]{f12.eps}
\caption{Simulated delay spectra amplitudes $|V_{b\tau}(\vec{b},\tau)|$ for the {\it off--zenith} pointing with all antenna spacings included ({\it top}) and with short eastward antenna spacings discarded ({\it bottom}). Discarded antenna spacings (black vertical stripes) have lengths $|\vec{b}|<30$~m (leftward of vertical dashed line) and orientations $|\theta_\textrm{b}|<$~22\fdg 5. The spillover from the bright Galactic center near the negative horizon delay limit from the {\it foreground wedge} prominent when all antenna spacings are used is lowered by an order of magnitude when short eastward antenna spacings are discarded. Color scale has been adjusted to emphasize mitigation achieved in foreground contamination. \label{fig:before-after}}
\end{figure}

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/baseline_screening_nside_64_Tsys_95.0K.eps}
\includegraphics[width=\linewidth]{f13.eps}
\caption{Drop in foreground contamination in the {\it EoR window}, and loss of data for the {\it off--zenith} pointing as a function of discarded baselines. Eastward baselines with varying degrees of directedness -- $|\theta_\textrm{b}|<$~7\fdg 5 (solid circles), $|\theta_\textrm{b}|<$~15\arcdeg~ (solid squares), and $|\theta_\textrm{b}|<$~22\fdg 5 (solid stars) -- and lengths $|\vec{b}| \le |\vec{b}|_\textrm{max}$ ($x$--axis) are discarded. Loss of data (dotted lines) is measured by discarded baselines as a fraction of the total number for the corresponding cases. Foreground contamination in the {\it EoR window} (solid lines) drops by a factor $\sim$1.5 ($|\theta_\textrm{b}|\le$~7\fdg 5) to $\sim$10 ($|\theta_\textrm{b}|\le$~22\fdg 5). The latter limit can be achieved with a mere 5\% loss of data at $|\vec{b}|_\textrm{max}\simeq30$~m, and discarding longer baselines ($|\vec{b}|\gtrsim 30$~m) has no effect in further reducing foreground contamination. \label{fig:screening}}
\end{figure}
